# Methods

As promised, here we reference the previous chapter, Chapter \@ref(review), using the chapter ID.


\TeX\ is the best way to typeset mathematics. Donald Knuth designed \TeX\ when he got frustrated at how long it was taking the typesetters to finish his book, which contained a lot of mathematics.  One nice feature of _R Markdown_ is its ability to read LaTeX code directly.

<!-- Unnumbered equation, use '$$' -->

$$
\hat{Y_i} = \beta_0 + \beta_1(X_{1i}) + \beta_2(X_{2i})
$$


<!-- To have a numbered equation, use the \begin{equation} and \end{equation} to embed your mathematics rather than '$$' -->

\begin{equation}
Y_i = \beta_0 + \beta_1(X_{1i}) + \beta_2(X_{2i}) + \epsilon_i
\end{equation}


## Figures


Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, echo=FALSE, fig.cap='Here is a nice figure!', out.width='60%', fig.asp=.75, fig.align='center', fig.pos='H'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). 

## Tables

The easiest way to create a table is to use Excel to input the information for your table and save it as a CSV file. Then you can read in the CSV file, and use the `kable()` function from **knitr** to style the table.

```{r nice-tab, echo=FALSE, message=FALSE}
#Read in data
gopher = readr::read_csv("data/tab-gopher-women-sports.csv")

# Create table
knitr::kable(
  gopher, 
  caption = "2017 Ticket Sales and Operating Revenue for the University of Minnesota Women's Athletic Teams",
  booktabs = TRUE
)
```

Further table styling can be carried out via the **kableExtra** package; see https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf. You can also reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).


\clearpage

<!-- clearpage ends the page, and also dumps out all floats.
 Floats are things like tables and figures. It is useful to inlcude this at the end of each chapter. -->

