# Methods

As promised, here we reference the previous chapter, Chapter \@ref(review), using the chapter ID.


<!-- Unnumbered equation, use '$$' -->

$$
\sum_{j=1}^n (\delta\theta_j)^2 \leq {{\beta_i^2}\over{\delta_i^2 + \rho_i^2}}
\left[ 2\rho_i^2 + {\delta_i^2\beta_i^2\over{\delta_i^2 + \rho_i^2}} \right] \equiv \omega_i^2
$$


<!-- To have a numbered equation, use the \begin{equation} and \end{equation} to embed your mathematics rather than '$$' -->

\begin{equation}
\pi(\theta|X_1< y_1,\dots,X_n<y_n) \varpropto \pi(\theta) \prod_{i=1}^n\int_{-\infty}^{y_i}
   \exp\left(-{(x-\theta)^2\over{2\sigma^2}}\right)\ dx
\end{equation}


## Figures


Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.pos='H'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). 

## Tables

The easiest way to create a table is to use Excel to input the information for your table and save it as a CSV file. Then you can read in the CSV file, and use the `kable()` function from **knitr** to style the table.

```{r nice-tab}
#Read in data
gopher = readr::read_csv("data/tab-gopher-women-sports.csv")

# Create table
knitr::kable(
  gopher, 
  caption = "2017 Ticket Sales and Operating Revenue for the University of Minnesota Women's Athletic Teams",
  booktabs = TRUE
)
```

Further table styling can be carried out via the **kableExtra** package; see https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf. Below we demonstrate some of that functionality.

```{r nice-tab-2}
library(kableExtra)

knitr::kable(
  gopher, 
  caption = "2017 Ticket Sales and Operating Revenue for the University of Minnesota Women's Athletic Teams",
  booktabs = TRUE,
  format = "latex"
  ) %>%
  footnote(general = "Data obtained from the 2017 NCAA Financial Report")
```

You can also create the table from within R itself and then use `kable()`.

```{r}
tab = flights %>%
  filter(month == 12, day == 24) %>%
  group_by(carrier_name) %>%
  summarize(
    Departure = mean(dep_delay),
    Arrival = mean(arr_delay)
    ) %>%
  select(Carrier = carrier_name, Departure, Arrival)

knitr::kable(
  tab, 
  caption = "Average Departure and Arrival Delay (in Minutes) by Carrier on Decemebr 24",
  booktabs = TRUE,
  format = "latex",
  digits = 2
  )
```



You can also reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).




